Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-23 Thesis/04-chap4.qmd
caption of fig 4.2

```{r fig-summary-plot, echo = TRUE, fig.height=3, fig.width=6, fig.cap="Summary plot comparing the densities of VSS for bootstrapped residual samples relative to VSS for null plots (blue)."}
checker$summary_plot()
```

>>>>

```{r fig-summary-plot, echo = TRUE, fig.height=3, fig.width=6, fig.cap="Summary plot comparing the densities of VSS for bootstrapped residual samples (red) relative to VSS for null plots (blue)."}
checker$summary_plot()
```
